Hypertension and microbiome

### 2019-10-21 articletwo.Rmd
Minor

```{r alphabeta definitions}
diversities <- diversities(pseq = pseq.species,
                           vars = list("max" = var.CL, "min" = var.CL.min),
                           betadiversity = adonis.species,
                           names.dset = names.dset)
```

@@

```{r talbe alpha div min}
diversities %>%
    map_df(~as.data.frame(.x), .id = "covariates") %>%
    mutate_if(is.numeric, round, 3) %>%
    kable
```

```{r save grob}
g4 <- plot.diversities(diversities)
ggsave(file = "cache/alpha-beta.png", plot=g4, height=6, width=9)
```

@@

Comparing how adding additional covariate to basic model for age, sex,
and hypertension changes number of significant associations found for
hypertension.

@@

@@

```{r supplement table for alpha diversity}
alphadiversity.table <- cbind(alphadiversity$min %>% dplyr::rename_all(paste0, ".min"),
                                  alphadiversity$max %>% dplyr::rename_all(paste0, ".max")) %>%
    dplyr::filter(model_name.min == model_name.max) %>%
    merge(names.dset, by.x ="response.min", by.y = "Covariate") %>%
    mutate(mean_ci.min = sprintf("%.2f (%.2f - %.2f)", estimate.min, conf.low.min, conf.high.min),
           pubp.min = pub.p(p.value.min),
           mean_ci.max = sprintf("%.2f (%.2f - %.2f)", estimate.max, conf.low.max, conf.high.max),
           pubp.max = pub.p(p.value.max)) %>%
    arrange(match(response.min, c("SYSTM", "DIASM", "MAP", "PULSEPRESSURE", "HT"))) %>%
    select(Name, mean_ci.min, pubp.min, mean_ci.max, pubp.max)

@@

```{r supplement table for beta diversity}
betadiversity.table <- merge(diversities$min %>% dplyr::rename_all(paste0, ".min"),
      diversities$max %>% dplyr::rename_all(paste0, ".max")) %>%
    dplyr::filter(response.min == response.max) %>%
    merge(names.dset, by.x ="response.min", by.y = "Covariate") %>%
    mutate(R2.min = sprintf("%.3f%%", R2.min*100),
           pubp.min = pub.p(R2.p.min),
           R2.max = sprintf("%.3f%%", R2.max*100),
           pubp.max = pub.p(R2.p.max)) %>%
    arrange(match(response.min, c("SYSTM", "DIASM", "MAP", "PULSEPRESSURE", "HT"))) %>%
    select(Name, R2.min, pubp.min, R2.max, pubp.max)

@@

```{r Write supplement}
doc.s <- read_docx(path = "style/articlestyle.docx") %>%
  body_remove()
#writetable(doc.s, core.names.flextable, number = "S1", "Core genera", "")
#writetable(doc.s, alphadiversity.flextable, number = "S2", "Alpha diverstity", "")
#writetable(doc.s, betadiversity.flextable, number = "S3", "Beta diverstity", "")
writetable(doc.s, deseq.flextable, number = "S4", "Deseq", "")
print(doc.s, target = paste0("report/articletwo-supplement.docx"))
```

>>>>

```{r alphabeta definitions}
diversity <- diversities(pseq = pseq.species,
                           vars = list("max" = var.CL, "min" = var.CL.min),
                           betadiversity = adonis.species,
                           names.dset = names.dset)
```

@@

```{r talbe alpha div min}
diversity %>%
    map_df(~as.data.frame(.x), .id = "covariates") %>%
    mutate_if(is.numeric, round, 3) %>%
    kable
```

```{r save grob}
g4 <- plot.diversities(diversity)
ggsave(file = "cache/alpha-beta.png", plot=g4, height=6, width=9)
```

@@

Comparing how adding additional covariate to basic model for age, sex,
and hypertension changes number of significant associations found for
hypertension. Full model has

`r sum(results(dds$HYPERTENSION, name = "HYPERTENSION_1_vs_0")$padj < 0.05, na.rm = TRUE)`

associations for hypertension.

@@

Listing our "core" genera

@@

Listing results for alpha diversity

```{r supplement table for alpha diversity}
alphadiversity.table <- diversity %>% map_df(~as.data.frame(.x), .id = "model") %>%
    mutate(mean_ci = sprintf("%.2f (%.2f - %.2f)", alpha.effect, alpha.low, alpha.high),
           pubp = pub.p(alpha.p)) %>%
    myspread(list = c2l("mean_ci", "pubp"), term = "Name", key = "model") %>%
    arrange(match(Name, c("Systolic BP", "Diastolic BP", "Mean arterial pressure", "Pulse pressure", "Hypertension"))) %>%
        select(Name, min_mean_ci, min_pubp, max_mean_ci, max_pubp)

@@

```{r supplement table for beta diversity}
betadiversity.table <- diversity %>% map_df(~as.data.frame(.x), .id = "model") %>%
    mutate(rsquared = sprintf("%.3f%%", beta.R2*100),
           pubp = pub.p(beta.p)) %>%
    myspread(list = c2l("rsquared", "pubp"), term = "Name", key = "model") %>%
    arrange(match(Name, c("Systolic BP", "Diastolic BP", "Mean arterial pressure", "Pulse pressure", "Hypertension"))) %>%
    select(Name, min_rsquared, min_pubp, max_rsquared, max_pubp)

@@

```{r Write supplement}
doc.s <- read_docx(path = "style/articlestyle.docx") %>%
  body_remove()
writetable(doc.s, core.names.flextable, number = "S1", "Core genera", "")
writetable(doc.s, alphadiversity.flextable, number = "S2", "Alpha diverstity", "")
writetable(doc.s, betadiversity.flextable, number = "S3", "Beta diverstity", "")
writetable(doc.s, deseq.flextable, number = "S4", "Deseq", "")
print(doc.s, target = paste0("report/articletwo-supplement.docx"))
```
